%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% SAMPLE_IJAM file
%%% For LaTeX users:


\documentclass[12pt]{article}
\usepackage{amsmath, amsthm}

\textwidth 12cm \textheight 18cm

%%% Theorem Like Envirouments

\newtheoremstyle{theorem}%name
{10pt} % space above
{10pt} % space below
{\sl} % bofy font
{\parindent} % ident - empty=no indent, \parindent= paragraph indent
{\bf} % thm head font
{. } % punctuation after thm head
{ } % space after thm head: `` ``=normal \newline=linebreak
{} % thm head specification
\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}

\newtheoremstyle{defi}%name
{10pt} % space above
{10pt} % space below
{\rm} % bofy font
{\parindent} % ident - empty=no indent, \parindent= paragraph indent
{\bf} % thm head font
{. } % punctuation after thm head
{ } % space after thm head: `` ``=normal \newline=linebreak
{} % thm head specification
\theoremstyle{defi}
\newtheorem{definition}[theorem]{Definition}

\def\proofname{\indent {\sl Proof.}}

%%%% Author's Definitions start here
% ..............
%%%% End of Author's Definitions

\begin{document} %%%%%%%%%%%%%%%%%%%%%%%%%%

\title{TITLE OF THE PAPER}

\author{First Author $^1$ , Second Author $^2$\\[6pt]
$^1$ First Author's Full Postal Address\\ The address must be written in English\\
Town - Postal Code, COUNTRY\\
e-mail: First Author's e-mail address\\[6pt]
$^2$ Second Author's Address\\ The address must be written in English\\
Town - Postal Code, COUNTRY \\ e-mail: Second Author's e-mail
address}

\maketitle

\begin{abstract}

Text of the abstract. Text of the abstract. Text of the
abstract.............................................................
...................................

\medskip

{\bf Math. Subject Classification:} ...

{\bf Key Words and Phrases:} ...

\end{abstract}

%%%%%%%% Section 1 %%%%%%%%%%%%%%%%%%%%
\section{First Section of the Paper}

Text ... (see \cite{gasrah}, \cite{rosbl}, \cite{Moak})...


\begin{definition}
Text of Definition 1.
\end{definition}

\begin{theorem}
Text of Theorem 1.
\end{theorem}

\begin{proof}
The proof of the theorem.
\end{proof}

\begin{corollary}
Text of Corollary 2.
\end{corollary}

%%%%%%%% Section 2 %%%%%%%%%%%%%%%%%%%%
\section{Second Section of the Paper}

Text ...

%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%
\begin{thebibliography}{99}

%% example for a book
\bibitem{gasrah} G. Gasper, M. Rahman,
{\it Basic Hypergeometric Series}, Cambridge University Press, Cambridge (1990).

%% example for paper in journal
\bibitem{Moak} D.S. Moak,
The $q$-analogue of the Laguerre polynomials, {\it J. Math. Anal. Appl.}, {\bf 81} (1981), 20-47.

%% example for paper in Proc. or Collected Works
\bibitem{rosbl} M. Rosenblum,
Generalized Hermite polynomials and the Bose-like oscillator
calculus, In: {\it Operator Theory: Advances and Applications},
Birkh\"auser, Basel (1994), 369-396.

\end{thebibliography}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%55
