%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% SAMPLE_IJAM file
%%% For LaTeX users:


\documentclass[12pt]{article}
%{article}
\usepackage{amssymb}
\usepackage{amsmath, amsthm}
\usepackage{amstext, amsfonts}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{wrapfig}

\newcommand{\dO}{\partial\Omega_{h}}

\textwidth 12cm \textheight 18cm

%%% Theorem Like Envirouments

\newtheoremstyle{theorem}%name
{10pt} % space above
{10pt} % space below
{\sl} % bofy font
{\parindent} % ident - empty=no indent, \parindent= paragraph indent
{\bf} % thm head font
{. } % punctuation after thm head
{ } % space after thm head: `` ``=normal \newline=linebreak
{} % thm head specification
\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}

\newtheoremstyle{defi}%name
{10pt} % space above
{10pt} % space below
{\rm} % bofy font
{\parindent} % ident - empty=no indent, \parindent= paragraph indent
{\bf} % thm head font
{. } % punctuation after thm head
{ } % space after thm head: `` ``=normal \newline=linebreak
{} % thm head specification
\theoremstyle{defi}
\newtheorem{definition}[theorem]{Definition}

\def\proofname{\indent {\sl Proof.}}

%%%% Author's Definitions start here
% ..............
%%%% End of Author's Definitions

\begin{document} %%%%%%%%%%%%%%%%%%%%%%%%%%

\title{New Boundary Condition for the Two Dimensional Stationary Boussinesq Paradigm Equation}

\author{K. Angelow $^1$ \\[6pt]
$^1$ angelow@math.bas.bg\\ 
Institute of Mathematics and Informatics\\
Bulgarian Academy of Sciences, Acad. G.~Bonchev Bl.8\\
Sofia - 1113, Bulgaria\\
e-mail: angelow@math.bas.bg\\[6pt] }

\maketitle

\begin{abstract}

In this paper the stationary propagating wave solution to the two dimensional Boussinesq equation is examined, which is a solution to a nonlinear fourth order elliptic equation.  We propose and apply a new boundary condition (BC) on the computational boundary. The numerical algorithm for computation of stationary propagating waves is based on high order accurate finite difference schemes. The performed numerical tests confirm the validity of the new BC. A comparison with the known in the literature formulas is also given. 

\medskip

%{\bf Math. Subject Classification:} ...

{\bf Key Words and Phrases:} stationary wave, Boussinesq equation, boundary, soliton, uniform grid, false transient method

\end{abstract}

%%%%%%%% Section 1 %%%%%%%%%%%%%%%%%%%%
\section{Introduction}
In this paper we consider stationary solutions (solutions of type  $u(x,y,t)=U(x,y - ct)$) to the two dimensional Boussinesq Paradigm Equation (BE) 

\begin{equation}
u_{tt} - \Delta u -\beta_1  \Delta u_{tt} +\beta_2 \Delta ^2 u + \Delta f(u)=0 \quad \text{for} (x,y) \in R^{+} ,\label{eq1}
\end{equation}
\begin{equation}\label{eq1B}
\begin{split}
&u(x,y,0)=u_0(x,y), \, u_t(x,y,0)=u_1(x,y)   \quad\text{for} \, (x,y) \in R^2, \\
&u(x,y) \rightarrow 0,  \Delta u(x,y) \rightarrow 0 ,  \quad \text{for}  \sqrt{x^2 + y^2} \rightarrow \infty, 
\end{split}
\end{equation}
where   $f(u)=\alpha u^2$,  $\alpha>0$, $\beta_1>0$, $\beta_2>0$  are dispersion parameters, and $\Delta$ is the Laplace operator. A derivation of the BE from the original Boussinesq system with discussion on the different mechanical properties could be found e.g. in \cite{ref1}. 
The one-dimensional (1D) BE is famous with its approximation for long waves propagating in shallow water \cite{ref2, ref3}. Furthermore, 1D BE admits localized wave solutions (called ‘solitons’), 
\begin{align}
&u_{tt} - u_{xx} -\beta_1  u_{xxtt} +\beta_2 u_{xxxx} + f_{xx}(u) =0, \label{eq2}
\end{align}
which maintain shape and emerge unchanged from collisions with other traveling waves, appear to be a very suitable model for particles \cite{ref4, ref5}.
We try to find a stationary, traveling in y direction with phase velocity c, wave solution to the 2D BE, i.e. a solution to \ref{eq1}, \ref{eq1B} of type $u(x,y,t)=U(x,y - ct)$. The waves U satisfy the nonlinear fourth order elliptic equation:
\begin{equation}
c^2 (E-\beta_1 \Delta) U_{yy} = \Delta U -\beta_2 \Delta^2 U - \Delta f(U), \label{eq3}
\end{equation}
where $E$ is the identity operator. If the condition  $c<min(1/\sqrt{\beta}, 1)$, $\beta = \beta_1/\beta_2$,   holds, then \ref{eq3} is an elliptic equation of fourth order and the linear second order derivatives in \ref{eq3} form a second order elliptic equation. In this paper we consider velocities $c$ which fulfill this inequality.
 The aim of this paper is to evaluate numerically the stationary soliton solution U to \ref{eq1}, i.e. the solution to \ref{eq3}. In the future, it is planned to investigate this solution as a candidate for a two dimensional ‘soliton-like’ solution of the nonstationary problem \ref{eq1} (to study the evolution in time of the shape of this solution and the collision of two solutions).
Different solution techniques have been applied through the investigation of the elliptic problem \ref{eq3}. The “False Transient Method” and the “Galerkin Spectral Method” are used in \cite{ref6,ref9} ; the “Fourier Galerkin Method” is implemented in \cite{ref8,ref9} and the “The Perturbation Solution” - in \cite{ref10}.
We emphasize that both problems, Eq. \ref{eq1} and Eq. \ref{eq3}, are posed on unbounded domain – the plane $R^2$. Thus we have to limit the domain of computation numerically so that the numerical solution will approximate the exact solution for the unbounded domain and, moreover, to keep the overall computational cost reasonable.
So we have to state an artificial boundary $Ω$ and artificial boundary conditions (BC), known in the literature as ‘absorbing’ boundary conditions (BC) or ‘nonreflecting’ BC (see \cite{ref11} for a wave equation, \cite{ref12} for a Helmholtz type equation, \cite{ref13} for elliptic second order equation, etc.). 
\\
The problem for posing artificial BC for BE is studied in \cite{ref6}, where first the following asymptotic of U is found
\begin{equation}
U(r) \sim  C_u/r^2, \text{for} >> 1\label{eq4}
\end{equation}
In this paper a new and more sophisticated artificial BC for stationary BE \ref{eq3}

\begin{equation}
U(r) =  \mu \frac{(1-c^2)x^2 - y^2}{(1-c^2)x^2 + y^2}|_{\dO}  \label{eq5}
\end{equation}
is proposed. The information about the known outer solution- the solution, valid for sufficiently large r, $ r=\sqrt{x^2 + y^2}\rightarrow \infty$  , is used. This condition has an analytical form, which directly depends on the velocity c. Furthermore, high order finite difference schemes are used for numerical evaluation of the solution to problem \ref{eq3}. The new BC \ref{eq5} and the numerical method are validated by performing a series of experiments, as mesh refinement and computations on different space domains. A comparison of the obtained here results with the similar results from  \cite{ref10} is also discussed. 

%%%%%%%% Section 2 %%%%%%%%%%%%%%%%%%%%
\section{Derivation of the new asymptotic boundary conditions }

Problem \ref{eq3} can be rewritten as a system of two elliptic equations of second order in different ways. We expect that the derivative   in x direction will be smaller than the derivative   in y direction because the solution moves along the y-axis. Therefore the equality   is substituted in \ref{eq3} and after introducing an auxiliary function W, we obtain an equivalent to \ref{eq3} system of two elliptic equations:

\begin{equation}\label{eq6}
\begin{split}
&(1-c^2) U + ( c^2\beta_1 -  \beta_2) \Delta U  - f (U) = W, \\ 
&\Delta W =  -c^2  (E- \beta_1 \Delta) U_{xx}. 
\end{split}
\end{equation}

We have to complete the system \ref{eq6} with appropriate boundary conditions for functions U and W. In \cite{ref6} the behavior of the solution U(r) for  $ r=\sqrt{x^2 + y^2}\rightarrow \infty$ is studied in details. From the mathematical analysis and numerical results provided there it follows that U(r) and W(r) have  $O(r^{-2})$ asymptotic decay at infinity. 
The main goal of this paper is to derive new implementation of these asymptotic conditions and to use them on the boundary of a truncated computational domain $\Omega_h$.
	We would like to go further by estimating which terms in the equations \ref{eq3},  define the asymptotic behavior and then validate our proposition by numerical tests. At first, suppose that for sufficiently large r the second order derivatives $\Delta U , c^2U_{xx} , c^2U_{yy}$  of U are of order  $O(r^{-4})$, whereas the fourth order derivatives and the nonlinear term, i.e.  $\Delta^2 U , c^2\Delta U_{xx} , c^2\Delta U_{yy}, \Delta f(U)$    in equation \ref{eq3} are of order $O(r^{-6})$.  
Now consider equation \ref{eq3} for sufficiently large values of r. We insert the asymptotic values of all terms in \ref{eq3} and neglect the higher order terms of order $O(r^{-6})$ inside the r-expansion. Thus for large values of r the following formulas are valid:
\begin{equation}
 \Delta \bar{U}(x,y) =   c^2   \bar{U}(x,y) , \quad  \bar{U}(x,y) \sim \frac{1}{x^2 + y^2} \quad \text{for} \quad x^2 + y^2 \rightarrow \infty  . \label{eq8}
\end{equation}


We apply the following change of variables
\begin{equation}
\bar{x} = \sqrt{1-c^2}x , \quad  \bar{y} = y, \quad \bar{v}( \bar{x}, \bar{y}) := \bar{U} (x, y)\label{eqVC}
\end{equation}
and transform \ref{eq8} into the Laplace equation for the new function $\bar{v}$
\begin{equation} \label{eqLap}
\bar{v} = 0, \quad \bar{v}( \bar{x}, \bar{y}) \sim \frac{1}{\bar{r}}, \quad |\bar{r}|=\sqrt{\bar{x}^2 + \bar{y}^2} \rightarrow \infty.
\end{equation}
In polar coordinates the Laplace equation \ref{eqLap} is rewritten as:
\begin{equation} \label{eqLapPol}
\frac{\partial^2}{\partial \bar{r}^2} \bar{v}(\bar{r}, \theta) + \frac{1}{\bar{r}} \frac{\partial}{\partial \bar{r}}\bar{v}(\bar{r}, \theta) +  \frac{1}{\bar{r}^2} \frac{\partial^2}{\partial \theta^2} \bar{v}(\bar{r}, \theta) = 0
\end{equation}

After the separation of variables $\bar{v}(\bar{r}, \theta) = H(\bar{r})G(\theta)$  we get the following general form of functions G and H 

\begin{align}
&H(\bar{r}) = \sum^{\infty}_{n=2} (\mu_{1,n} \frac{1}{ \bar{r}^n} + \mu_{2,n} \bar{r}^n ),
\\ \nonumber &G(\theta) = \sum^{\infty}_{n=2} (\mu_{3,n}sin(n \theta ) + \mu_{4,n}cos(n \theta)). \label{eq9}
\end{align}
We fix the parameters $\mu_{2,i}, i \geq 2$  to zero because of the asymptotic limitation that $H(\bar{r}) \sim \frac{1}{\bar{r}^2} $  for $|\bar{r}| \rightarrow \infty $.
For simplicity we take into account the main term in the expansion of $H(\bar{r})$ and set $\mu_{1,i}, i \geq 3$  to zero. Analogously we set $\mu_{3,i}, i \geq 3$ and $\mu_{4,i}, i \geq 3$
to zero.  Further artificial simplification is made by setting $\mu_{3,2} = 0$. In this way the following representation of the main asymptotic term $\bar{v}$ is obtained:

\begin{equation}
\bar{v}(\bar{r} \theta) = \mu \frac{cos(2 \theta)}{ \bar{r}^2 } = 
 \mu \frac{cos(\theta) ^ 2 - sin(\theta)^2}{ \bar{r}^2 } = 
 \mu \frac{\bar{x}  ^ 2 - \bar{y}  ^ 2}{( \bar{x}  ^ 2 + \bar{y}  ^ 2)^2 } , \label{eq10}
\end{equation}

where $\mu = \mu_{1,2} \mu_{4,2}$. In the old (x, y) coordinate system, \ref{eq10}  reads as:

\begin{equation}
U(x,y) = \mu \frac{(1-c^2)x^2 - y^2}{ ( (1-c^2)x^2 + y^2 )^2 }. \label{eq12}
\end{equation}

We treat the second function W from \ref{eq6}  in a similar way and obtain similar  asymptotical representation

\begin{equation}
W(x,y) = \hat{\mu} \frac{(1-c^2)x^2 - y^2}{ ( (1-c^2)x^2 + y^2 )^2 }. \label{eq13}
\end{equation}



\begin{definition}
Text of Definition 1.
\end{definition}

\begin{theorem}
Text of Theorem 1.
\end{theorem}

\begin{proof}
The proof of the theorem.
\end{proof}

\begin{corollary}
Text of Corollary 2.
\end{corollary}

%%%%%%%% Section 2 %%%%%%%%%%%%%%%%%%%%
\section{Second Section of the Paper}

Text ... (see \cite{gasrah}, \cite{rosbl}, \cite{Moak})...

%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%
\begin{thebibliography}{99}

%% example for a book
\bibitem{gasrah} G. Gasper, M. Rahman,
{\it Basic Hypergeometric Series}, Cambridge University Press, Cambridge (1990).

%% example for paper in journal
\bibitem{Moak} D.S. Moak,
The $q$-analogue of the Laguerre polynomials, {\it J. Math. Anal. Appl.}, {\bf 81} (1981), 20-47.

\bibitem{ref1} C. I. Christov, An energy-consistent dispersive shallow-water model,  {\it Wave Motion }, 34, (2001) 161 - 174
\bibitem{ref2} Boussinesq, J. (1871). “Theorie de l’intumescence liquide, applelee onde solitaire ou de translation, se propageant dans un canal rectangulaire”,  {\it Comptes Rendus de l’Academie des Sciences } 72: 755-759

\bibitem{ref3} Boussinesq, J. (1872). “Theorie des ondes et des remous qui se propagent le long d’un canal rectangulaire horizontal, en communiquant au liquide contenu dans ce canal des vitesses sensiblement pareilles de la surface au fond”, {\it Journal de Mathematiques Pures et Aplliquees}, Deuxieme Serie 17: 55-108

\bibitem{ref4} I. Christov, C.I.Christov, Physical dynamics of quasi-particles in nonlinear wave equations, arxiv.org/pdf/nlin/0612005

\bibitem{ref5} J. K. Perring, T. H. R. Skyrme, A model unified field equation, {\it Nuclear Physics},  31 (1962) p. 550-555 

\bibitem{ref6}  C. I. Christov, Numerical implementation of the asymptotic boundary conditions for steadily propagating 2D solitons of Boussinesq type equations, {\it Mathematics and Computers in simulation}, 82 (2012), p. 1079-1092

\bibitem{ref7}  J. Choudhury, C. Christov, 2D Solitary waves of Boussinesq equation, AIP Conference Proceedings (2005), Volume 755, Issue 1, p. 85 - 90

\bibitem{ref8}  M. Christou, C. I. Christov, Fourier Galerkin method for 2D solitons of Boussinesq equation,  {\it Mathematics and Computers in Simulation} 74 (2007) p. 82 - 92

\bibitem{ref9}   M. Christou, C. I. Christov, Galerkin Spectral Method for the 2D Solitary Waves of Boussinesq Paradigm Equation, AIP Conference Proceedings (2009), Volume 1186, Issue 1, p. 217 - 225

\bibitem{ref10} C. I. Christov, J. Choudhury, Perturbation solution for the 2D Boussinesq equation,{\it Mech. Res. Commun. }, 38 (2011) p. 274 - 281

\bibitem{ref11} B. Engquist and A. Majda, Absorbing boundary conditions for the numerical simulation of waves, {\it Math. Comp.}, 31 (1977), p. 629–651.

\bibitem{ref12}  C. I. Goldstein, A finite element method for solving Helmholtz type equations in waveguides and other unbounded domains, {\it Math. Comp.}, 39 (1982), p. 309–324.

\bibitem{ref13}  H.Han, W. Bao, Error estimates for the finite element approximation of problems in unbounded domains,  {\it SIAM J. NUMER. ANAL.} 37, No. 4, p. 1101–1119

\bibitem{ref14} N. Kolkovska, Two Families of Finite Difference Schemes for Multidimensional Boussinesq Paradigm Equation, AIP Conference Proceedings (2010), Volume 1301, p. 395 http://dx.doi.org/10.1063/1.3526638

\bibitem{ref15} N. Kolkovska, K. Angelow, Numerical Computation of the Critical Energy Constant for Two-dimensional Boussinesq Equations,  AIP Conference Proceedings, Volume 1684, 080007-1–080007-6; doi: 10.1063/1.4934318

\bibitem{ref16} P.Northrop, P.A.Ramachandran, W.Schiesser, V. R.Subramanian, A robust false transient method of lines for elliptic partial differential equations, Chemical Engineering Science 90 (2013) 32–39


%% example for paper in Proc. or Collected Works
\bibitem{rosbl} M. Rosenblum,
Generalized Hermite polynomials and the Bose-like oscillator
calculus, In: {\it Operator Theory: Advances and Applications},
Birkh\"auser, Basel (1994), 369-396.

\end{thebibliography}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%55
